The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars

### 2019-05-17 paper/ms.tex
updates

To estimate \Dnu, we divided the power spectrum by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian. We fit and report also the dimensionless parameter $\epsilon$ is the offset of the lowest frequency in the comb of p-modes from zero frequency in units of $\Dnu$.

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. 
We also calculate \gaia-like stellar bolometric radii using the software \texttt{isoclassify} \citep{huber2017}, using as our input \teff values our new spectroscopic \teff, \feh, and \logg measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes, and SIMBAD $V$. While not all of our targets have radii in the \gaia catalogs, for those that do we find that there is overall agreement to within a few $\sigma$, but that the results from stellar modelling are consistently slightly larger than those from \gaia. 
This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely due to noise. Agreement for large-radius ($>30 \rsun$) stars is somewhat poorer, even though the \gaia parallax-over-error is apparently adequate. This dispersion, unlike for medium radius stars, is more pronounced for the \texttt{isoclassify} radii than for \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

To facilitate open science, we have made the products of this research available online. All code used to produce smear light curves is available under a GPL~v3 license at \href{https://github.com/benjaminpope/keplersmear}{\nolinkurl{github.com/benjaminpope/keplersmear}}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

>>>>

To estimate \Dnu, we divided the power spectrum by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian. We also fit the dimensionless parameter $\epsilon$, which is the offset of the lowest frequency in the comb of p-modes from zero in units of $\Dnu$.

@@

To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax. 
We also calculate \gaia-like stellar bolometric radii using the software \texttt{isoclassify} \citep{huber2017}, using our new spectroscopic \teff, \feh, and \logg measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes, and SIMBAD $V$. While not all of our targets have radii in the \gaia catalogs, for those that do we find that there is overall agreement to within a few $\sigma$, but that the results from stellar modelling are consistently slightly larger than those from \gaia. 
This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration. Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling. It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax. Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely due to noise. Agreement for large-radius ($>30 \rsun$) stars is somewhat poorer, even though the \gaia parallax-over-error is apparently adequate. This dispersion, unlike for medium radius stars, is more pronounced for the \texttt{isoclassify} radii than for \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.

@@

To facilitate open science, we have made the products of this research available online. All code used to produce smear light curves is available under a GPL~v3 license\footnote{ \href{https://github.com/benjaminpope/keplersmear}{\nolinkurl{github.com/benjaminpope/keplersmear}} \citep{keplersmear_zenodo}}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High Level Science Product\footnote{\dataset[10.17909/t9-4sgf-9c19]{\doi{10.17909/t9-4sgf-9c19}}}. TRES spectra are available from the ExoFOP-TESS website\footnote{\dataset[exofop.ipac.caltech.edu/tess/]{https://exofop.ipac.caltech.edu/tess/}}.
